### 2020-08-25 code/figure9.Rmd
Update axis title to figure 8&9, add legend for SM2

kclassplot = function(dfsamps,tisnames){
	kclnames = grep("k\\[",names(dfsamps), value=TRUE)
	dfclas = dfsamps[,kclnames]
	dfclas = stack(dfclas)
	names(dfclas) = c("value","coefname")
	dfclas$class = as.factor(as.numeric(gsub("k\\[(.*),(.*)\\]","\\2",dfclas$coefname)))
	dfclas$tiss = tisnames[as.numeric(gsub("k\\[(.*),(.*)\\]","\\1",dfclas$coefname))]
	ggplot(dfclas,aes_(quote(value),quote(class), fill = quote(class))) + geom_density_ridges() +
		facet_wrap(. ~ tiss,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
		xlim(0,3) + theme(legend.position = "none") + ggtitle("Class Specific Coefficients")
}

>>>>

kclassplot = function(dfsamps,tisnames){
	kclnames = grep("k\\[",names(dfsamps), value=TRUE)
	dfclas = dfsamps[,kclnames]
	dfclas = stack(dfclas)
	names(dfclas) = c("value","coefname")
	dfclas$class = as.factor(as.numeric(gsub("k\\[(.*),(.*)\\]","\\2",dfclas$coefname)))
	dfclas$tiss = tisnames[as.numeric(gsub("k\\[(.*),(.*)\\]","\\1",dfclas$coefname))]
	ggplot(dfclas,aes_(quote(value),quote(class), fill = quote(class))) + geom_density_ridges() +
		facet_wrap(. ~ tiss,nrow=3) + theme_minimal() + scale_fill_brewer(palette = "Paired") +
		xlim(0,3) + theme(legend.position = "none") + ggtitle("Class Specific Coefficients") +
	  labs(x = expression(paste("k"["cl"])), y = "Cluster Identity")
}
